Test

### 2019-01-17 eyeIntegration_app_manuscript.Rmd
demo table and fig
template messing around

---
title: Test
author: |
  | $^1$OGVFB NEI NIH
  | David M McGaughey 1^[Corresponding author: mcgaugheyd@mail.nih.gov] $^1$, John M Bryan $^1$
abstract: |
  eyeIntegration is an series of open databases with an extensive transcriptomic database containing over 30 GTEx human body tissues as well as major components of the eye: retina, RPE, RPE-choroid, and cornea. eyeIntegration also holds two WGCNA networks for retina and RPE-choroid. Web application.
bibliography: Unified Gene Expression.bib
csl: genome-biology.csl
output:
  bookdown::pdf_document2:
  toc: yes
  word_document: default
fig_caption: yes
always_allow_html: yes
header-includes:
    - \usepackage{setspace}
    - \doublespacing
    - \usepackage{lineno}
    - \linenumbers
---

@@

# Materials and Methods

## 
## Single Cell RNA-Seq Data
[@macoskoHighlyParallelGenomewide2015]

>>>>

---
title: Test
author: |
  | $^1$OGVFB NEI NIH
  | David M McGaughey 1^[Corresponding author: mcgaugheyd@mail.nih.gov] $^1$, John M Bryan $^1$
abstract: |
  eyeIntegration is an series of open databases with an extensive transcriptomic database containing over 30 GTEx human body tissues as well as major components of the eye: retina, RPE, RPE-choroid, and cornea. eyeIntegration also holds two WGCNA networks for retina and RPE-choroid. Web application.
bibliography: Unified Gene Expression.bib
csl: genome-biology.csl
output:
  word_document:
    reference_docx: word-styles-reference-01.docx 
fig_caption: yes
always_allow_html: yes
header-includes:
    - \usepackage{setspace}
    - \doublespacing
    - \usepackage{lineno}
    - \linenumbers
---

@@

```{r, fig.cap=paste('Density of num'), echo=F}
library(tidyverse)
rand <- sample(1:100, 100, replace=F)
rand %>% density() %>% plot()
```
# Materials and Methods

Cell | Number
----- | -----
RPE | 200
Fibroblast | 30

## Single Cell RNA-Seq Data
[@macoskoHighlyParallelGenomewide2015]
